Slitasje og kjørespor

### 2023-01-19 DRAFT_slitasjeOgKjørespor.Rmd
feat: bbox for Trondheim

Let's calculate the areas of these polygons and compare the HIF in the five regions. 
```{r HIF-region, fig.cap="Stacked barplot showing the distribution of human impact factor across five regions in Norway."}
HIA_regions$area <- sf::st_area(HIA_regions)

@@

@@

Now let's check the correlation between the HIF and the indicator values. 
```{rslitasje-box, fig.cap="The relationship between human impact factor (a categorical version of the Norwegian Infrastructure Index) and the indicator avleus for slitasje."}
ggplot(slitasje_data_extrapolated, aes(x = factor(HIF), y = meanIndicatorValue))+
  geom_boxplot(fill = "grey",
               size=1.5)+
  theme_bw(base_size = 12)+
  labs(x = "Human Impact Factor", y = "Slitasje indicator value")
```

>>>>

Let's calculate the areas of these polygons and compare the HIF in the five regions. 
First we need to remove some marine areas.
```{r}
HIA_regions2 <- HIA_regions %>%
  st_intersection(outline)
```

```{r HIF-region, fig.cap="Stacked barplot showing the distribution of human impact factor across five regions in Norway."}
HIA_regions$area <- sf::st_area(HIA_regions)

@@

It's easier to see what's happening if we zoom in a bit.
Lets get a boundary box around Trondheim.

```{r}
myBB <- st_bbox(c(xmin=260520.12, xmax = 278587.56,
                ymin = 7032142.5, ymax = 7045245.27),
                crs = st_crs(slitasje_data_extrapolated))
```

Cropping the raster to the bbox

```{r}
slitasje_data_extrapolated_trd <- sf::st_crop(slitasje_data_extrapolated, myBB)
```

Get map of major roads, for context
```{r}
hw_utm <- readRDS("data/cache/highways_trondheim.rds")
```

```{r}
tm_shape(slitasje_data_extrapolated_trd)+
  tm_polygons(col = "meanIndicatorValue",
    title="Slitasje indicator",
    palette = "viridis",
    style="cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")
```

@@

Now let's check the correlation between the HIF and the indicator values.
<!-- This is not correct. This count the polygins that have very different sizes -->

```{r slitasje-box, fig.cap="The relationship between human impact factor (a categorical version of the Norwegian Infrastructure Index) and the indicator avleus for slitasje."}
ggplot(slitasje_data_extrapolated, aes(x = factor(HIF), y = meanIndicatorValue))+
  geom_boxplot(fill = "grey",
               size=1.5)+
  theme_bw(base_size = 12)+
  labs(x = "Human Impact Factor", y = "Slitasje indicator value")
```
